Windowed least-squares model reduction for dynamical systems

### 2019-10-06 main.tex
update

\subsection{\spatialAcronym\ trial subspaces}
\spatialAcronym\ trial subspaces approximate the FOM ODE solution
	$\stateFOM(t)$, $t\in[0,T]$ with an approximation $\approxstate(t)$, $t\in[0,T]$ that resides in an
	affine space--time trial subspace of dimension $K\ll\fomdim$, i.e., 
	$\approxstate\in \stspaceS$, where
\begin{equation}\label{eq:spatial_subspace}
\begin{split}
& \stspaceS \defeq \trialspace \otimes \timeSpace +
	\stateIntercept\otimes\onesFunction.\\ 
\end{split}
\end{equation}
Here, $\trialspace\subseteq\RR{\fomdim}$ with $\dim(\trialspace) = K$ denotes
the spatial trial subspace spanned by an orthogonal basis such that
$ \trialspace= \Range{\basismat}$
with 
$ \basismat \equiv \begin{bmatrix}  \basisvec_1  & \cdots &  \basisvec_K \end{bmatrix}
	\in \RRStar{\romdim}{\fomdim}$, where $\RRStar{\romdim}{\fomdim}$ denotes the compact Stiefel manifold (i.e.,  $
	\RRStar{\romdim}{\fomdim}\defeq
	\{ \mathbf{X} \in \RR{\fomdim
	\times \romdim}\, \big|\, \mathbf{X}^T \mathbf{X} = \mathbf{I} \}$).
%	$\timeSpace$ denotes the set of real-valued functions acting on the time
%	domain
%	$[0,T]$, 
We have also introduced $\onesFunction\in\timeSpace$ as the function $\onesFunction:\timeDummy\mapsto 1$
and
	$\stateIntercept \in \mathbb{R}^{\fomdim}$ as the reference state, which
	is often taken to be the initial condition (i.e., $\stateIntercept = \stateFOMIC$). 
%where $\basisvec_i \in \mathbb{R}^N$ are orthonormal basis vectors and $\stateIntercept \in \mathbb{R}^{\fomdim}$ the ``intercept''.
%We refer to $\basismat \in \RRStar{\fomdim \times \romdim}$, with $\RRStar{p \times q}$ denoting the set of orthogonal $q$ frames in $p$, as the spatial trial basis, and $\trialspace$ as the spatial trial space. 
The basis vectors $\basisvec_i$, $i=1,\ldots,K$ are typically constructed
using state snapshots, e.g., via
proper orthogonal decomposition (POD)~\cite{berkooz_turbulence_pod}, the reduced-basis method~\cite{rb_1,rb_2,rb_3,NgocCuong2005,Rozza2008}. 
At any time instance $t\in[0,T]$, ROMs that employ the  \spatialAcronym\ trial subspace approximate the state as
\begin{equation}\label{eq:affine_trialspace}
\stateFOMArg{}{t} \approx \approxstate(t) = \basisspace \genstateArg{}{t} + \stateIntercept,
\end{equation}
where $\genstate \in \RR{\romdim} \otimes \timeSpace$ with
$\genstate:\timeDummy\mapsto\genstate(\timeDummy)$
denotes the generalized
coordinates. Substituting the approximation~\eqref{eq:affine_trialspace} into the FOM ODE~\eqref{eq:FOM} and performing orthogonal
$\elltwo$-projection of the initial condition onto the trial subspace yields
the overdetermined system of ODEs
\begin{equation}\label{eq:g_truncation}
\basisspace \genstateDotArg{}{t} = \velocity(\basisspace
\genstateArg{}{t} + \stateIntercept,t ), \qquad \genstate(0) = \genstateIC,
	\qquad t \in [0,T],
\end{equation}
where $\genstateDot\equiv {d \genstate}/{d\tau}$.
Because Eq.~\eqref{eq:g_truncation} is overdetermined, a solution may not
exist. Typically, either \textit{Galerkin projection} or \textit{least-squares
Petrov--Galerkin projection} is employed to reduce the number of equations
such that a unique solution exists. We now describe these two methods.

@@

\KTC{HERE}
The LSPG method substitutes the \spatialAcronym\ trial subspace approximation
minimizes the residual of the FOM O$\Delta$E~\eqref{eq:lms} within the trial subspace over each time step. %We define the discrete residual for the implicit Euler method at the $n$th time-instance as,
%\begin{align*}
%\resid_{\text{IE}} & \vcentcolon (\stateyDiscrete;\stateFOMDiscreteArg{n-1}) \mapsto \frac{\stateyDiscrete - \stateFOMDiscreteArg{n-1}  }{\Delta t} -  \velocity(\stateyDiscrete), \\
%& \vcentcolon \RR{\fomdim} \times \RR{\fomdim} \rightarrow \RR{\fomdim}. 
%\end{align*}
The LSPG method is defined as follows,
\begin{equation*}
\approxstateLSPG^n = \underset{\stateyDiscrete \in \trialspace  }{\text{arg\,min}}|| \lspgWeightingArg{\stateyDiscrete}\residLMSArg{n} (\stateyDiscrete; \approxstateLSPG^{n-1},\ldots,\approxstateLSPG^{n-k^n}) ||_2^2, \qquad n = 1,2,\hdots,\ntimeSteps,
\end{equation*}
where $\approxstateLSPG^n \approx \stateFOMDiscreteArg{n}$ denotes the LSPG approximation to the state at $n$th time-step instance and 
$\lspgWeightingArg{\cdot} \in \RR{\nsamples \times \fomdim}$, with $\romdim \le \nsamples \le \fomdim$, is a weighting matrix that can be used, e.g., for hyper-reduction. 
Although illustrated for linear multistep methods, LSPG can be 
formulated for \textit{any} type of time-marching scheme (see Ref.~\cite{carlberg_lspg_v_galerkin} for, e.g., Runge--Kutta schemes).

In general, the LSPG approach has been observed to be more stable and accurate than the 
Galerkin approach~\cite{carlberg_lspg_v_galerkin,carlberg_thesis,carlberg_gnat}. The common interpretation of the improved performance of the LSPG method over the Galerkin method is that LSPG minimizes the residual over a finite-sized time window, while Galerkin minimizes only the instantaneous residual~\cite{carlberg_lspg_v_galerkin}.  
However, for general non-self-adjoint and nonlinear problems, LSPG, lacks \textit{a priori} guarantees of stability, accuracy, and convergence. Further, 
LSPG is sensitive to the time step: changing the time step changes the window over which the residual is minimized 
\textit{as well as} the temporal discretization error. As a result, optimal results are obtained at an intermediary time-step. 
For too small a time-step, the accuracy and stability of LSPG is similar to Galerkin; in the 
limiting case of $\Delta t \rightarrow 0$, LSPG recovers Galerkin~\cite{carlberg_lspg_v_galerkin}. 
For too large a time-step, the accuracy of LSPG degrades~\cite{carlberg_lspg_v_galerkin,parish_apg}. The 
precise reason for this degradation in accuracy is difficult to discern as increasing the time-step changes both the error incurred by 
temporal discretization and the window the residual is being minimized over. Lastly, LSPG is sensitive to the time-marching scheme: changing the 
time-marching scheme modifies the minimization problem. For example, LSPG reverts to a Galerkin approach 
when used with an explicit time-marching scheme. It is emphasized that, despite these challenges, 
LSPG is arguably the most popular reduced-order modeling technique for general nonlinear systems.

\subsection{\spaceTimeAcronym\ trial spaces and space--time ROMs}
Recent work has investigated space--time reduced-order models~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC,benner_st,bui_thesis}. Space--time methods 
are advantageous in that they allow for both spatial \textit{and} temporal dimension reduction. Further, space--time 
methods are often equipped with more favorable error bounds than non-space--time methods. The approach proposed in this work displays commonalities 
with space--time methods and, as such, we briefly outline \spaceTimeAcronym\ trial subspaces and space--time LSPG.

Space--time methods leverage the \spaceTimeAcronym\ trial subspace $\stspaceST$,
\begin{equation}\label{eq:sttrialspace_def}
 \approxstateArgnt{} \in  \stspaceST \subseteq \RR{N} \otimes \timeSpace,
\end{equation}
and the space--time trial basis \textit{functions},
\begin{align*}
\stbasisArgnt{} &: t \mapsto \stbasis(t) \\
 &: [0,T] \rightarrow  \RR{N \times \stdim} ,%\spaceTrialSpace , \\
%&  \in \RR{N \times \stdim} \otimes \timeTrialSpaceArg{},  
\end{align*}
with $\Range{\stbasis} + \stateInterceptArg{} \equiv \stspaceST$ and where $\stdim$ is the dimension of the space--time generalized coordinates.
%with $\mathbb{V}_{\stdim}( \RR{N} )$ denoting the set of orthogonal $\stdim$ frames in $\RR{N}$ (e.g., an $N \times \stdim$ matrix with orthogonal column vectors).
The state is approximated by,
\begin{equation}\label{eq:stapprox1}
 \stateFOMArg{}{t} \approx \approxstateArg{}{t}  = \stbasisArg{}{t} \stgenstate + \stateInterceptArg{},
\end{equation}
%where $\stbasisArgnt{} : \RR{\stdim} \rightarrow \spaceTrialSpace \otimes \timeTrialSpaceArg{}$ with $ \stbasisArgnt{n} \in \RR{N \times \stdim} \otimes \timeTrialSpaceArg{n}$ is the space--time trial basis, 
where $\stgenstateArg{} \in \RR{\stdim}$ are the space--time generalized coordinates. Critically, the 
space--time basis matrix comprises time-dependent \textit{functions}, while the generalized coordinates are a stationary vector. This is fundamentally different than  
\spatialAcronym\ trial subspaces, in where the generalized coordinates are time-dependent functions while the basis matrix is stationary.

Substituting the approximation~\eqref{eq:stapprox1} into the FOM ODE~\eqref{eq:FOM},
\begin{equation}\label{eq:st_fom}
\stbasisDotArg{}{t} \stgenstate =  \velocity(\stbasisArg{}{t} \stgenstate + \stateIntercept,t) , \qquad \genstate(0) =\mathbb{P}(\stateFOM)(0), \qquad t \in [0,T],
\end{equation}
where $\mathbb{P} : \RR{N} \otimes \timeSpace \rightarrow \stspaceST$ is an orthogonal projection onto the trial subspace (e.g., $\elltwo$).
Equation~\eqref{eq:st_fom} is an over-determined algebraic system for the $\stdim$ unknowns. We now outline the Space--Time Least-Squares Petrov--Galerkin method~\cite{choi_stlspg}. 
The space--time Galerkin method is noted to additionally be a possibility for model reduction. As the space--time Galerkin method does not associate with any residual minimization 
principle, however, we do not outline it here.
\subsubsection{Space--Time LSPG projection}  
As in LSPG, Space--Time LSPG (ST-LSPG)~\cite{choi_stlspg} minimizes the fully discrete residual, with the key difference being that ST-LSPG minimizes the residual over the entire time domain. For brevity, ST-LSPG is outlined only for linear multistep methods.
%As ST-LSPG acts on the discrete solution, we first note that the discrete FOM solution lives in $\RR{N} \otimes \RR{N_t}$. ST-LSPG then seeks solutions in the trial space,
%$$\stspaceDiscrete \defeq \spaceTrialSpace \otimes \timeTrialSpaceDiscrete \subseteq \RR{N} \otimes \RR{N_t},$$
%where $\timeTrialSpaceDiscrete$ is the discrete temporal trial space. It is noted that this trial space is a specific instance of the trial space~\ref{eq:sttrialspace_def} 
%As before, we define a discretization of the continuous time-domain $[0,T]$ into $N_t$ time instances $t^n = n\Delta t, n=1,2,\ldots,N_t$ with a constant time-step $\Delta t = T/N_t$. We define now the space--time discrete residual for the implicit Euler method as,
We first define the space--time discrete residual for linear multistep methods,
\begin{align*}
\residST_{} & \vcentcolon (\stateyDiscreteArg{N_t}, \ldots ,\stateyDiscreteArg{1};\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{N_t}(\stateyDiscreteArg{N_t};\stateyDiscreteArg{N_t-1},\ldots,\stateyDiscreteArg{N_t - k^{N_t}}) \\ 
%\frac{\stateyDiscreteArg{N_t-1} - \stateFOMDiscreteArg{N_t-2}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t-1}) \\
\vdots \\
%\frac{\stateyDiscreteArg{1} - \stateFOMIC }{\Delta t} -  \velocity(\stateyDiscreteArg{1}) \\
\residLMSArg{1}(\stateyDiscreteArg{1}; \stateFOMIC) 
\end{bmatrix}  \\
& \vcentcolon \RR{\fomdim} \otimes \RR{N_t+1} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
For convenience we define the same residual with the generalized coordinates as the inputs,
\begin{align*}
\genresidST_{\text{}} & \vcentcolon (\stgenstatey ;\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{n}\bigg( \stbasisArg{}{t^{N_t}}\stgenstatey + \stateIntercept; \stbasisArg{}{t^{N_t-1}}\stgenstatey + \stateIntercept ,\ldots,  \stbasisArg{}{t^{N_t-k^{N_t}}}\stgenstatey + \stateIntercept \bigg) \\ 
\vdots \\
\residLMSArg{n}\bigg( \stbasisArg{}{t^1}\stgenstatey + \stateIntercept; \stateFOMIC \bigg) \\ 
\end{bmatrix}  \\
& \vcentcolon \RR{\stdim} \times \RR{N} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
ST-LSPG is defined as,
\begin{equation*}
\stgenstate = \underset{ \stgenstatey }{\text{arg\,min}}|| \lspgWeightingSTArg{\stgenstatey}  \genresidST_{\text{}}(\stgenstatey;\stateFOMIC) ||_2^2, 
\end{equation*}
where $\lspgWeightingSTArg{\cdot} \in \RR{n_{st} \times N N_t}$, with $\stdim \le n_{st} \le N N_t$, is a space--time weighting matrix.

>>>>

\subsection{\spatialAcronym\ trial subspaces}
At a given time instance 
$t\in[0,T]$,
\spatialAcronym\ trial subspaces approximate the FOM ODE solution
	as $\approxstate(t)\approx\stateFOM(t)$, which is enforced to reside in an
	affine spatial trial subspace of dimension $K\ll\fomdim$ such that
	$\approxstate(t)\in
	\stateIntercept+\trialspace
\subseteq\RR{\fomdim}$, where $\dim(\trialspace) = K$
and $\stateIntercept \in \mathbb{R}^{\fomdim}$ denotes the reference state, which
	is often taken to be the initial condition (i.e., $\stateIntercept = \stateFOMIC$).
Here, the trial subspace
$\trialspace$ 
is spanned by an orthogonal basis such that
$ \trialspace= \Range{\basismat}$
with 
$ \basismat \equiv \begin{bmatrix}  \basisvec_1  & \cdots &  \basisvec_K \end{bmatrix}
	\in \RRStar{\romdim}{\fomdim}$, where $\RRStar{\romdim}{\fomdim}$ denotes the compact Stiefel manifold (i.e.,  $
	\RRStar{\romdim}{\fomdim}\defeq
	\{ \mathbf{X} \in \RR{\fomdim
	\times \romdim}\, \big|\, \mathbf{X}^T \mathbf{X} = \mathbf{I} \}$).
The basis vectors $\basisvec_i$, $i=1,\ldots,K$ are typically constructed
using state snapshots, e.g., via
proper orthogonal decomposition (POD)~\cite{berkooz_turbulence_pod}, the reduced-basis method~\cite{rb_1,rb_2,rb_3,NgocCuong2005,Rozza2008}. 
Thus, at any time instance $t\in[0,T]$, ROMs that employ the  \spatialAcronym\ trial subspace approximate the state as
\begin{equation}\label{eq:affine_trialspace}
\stateFOMArg{}{t} \approx \approxstate(t) = \basisspace \genstateArg{}{t} + \stateIntercept,
\end{equation}
where $\genstate \in \RR{\romdim} \otimes \timeSpace$ with
$\genstate:\timeDummy\mapsto\genstate(\timeDummy)$
denotes the generalized
coordinates.

	From the space--time perspective, this is equivalent to approximating the
	FOM ODE solution trajectory $\stateFOM\in\RR{N}\otimes\timeSpace$ with 
	$\approxstate\in \stspaceS$, where
\begin{equation}\label{eq:spatial_subspace}
\begin{split}
& \stspaceS \defeq \trialspace \otimes \timeSpace +
	\stateIntercept\otimes\onesFunction\subseteq\RR{N}\otimes\timeSpace
\end{split}
\end{equation}
with
	$\dim(\stspaceS) = K\ntimeSteps$
and $\onesFunction\in\timeSpace$ defined as
$\onesFunction:\timeDummy\mapsto 1$.

Substituting the approximation~\eqref{eq:affine_trialspace} into the FOM ODE~\eqref{eq:FOM} and performing orthogonal
$\elltwo$-projection of the initial condition onto the trial subspace yields
the overdetermined system of ODEs
\begin{equation}\label{eq:g_truncation}
\basisspace \genstateDotArg{}{t} = \velocity(\basisspace
\genstateArg{}{t} + \stateIntercept,t ), \qquad \genstate(0) = \genstateIC,
	\qquad t \in [0,T],
\end{equation}
where $\genstateDot\equiv {d \genstate}/{d\tau}$.
Because Eq.~\eqref{eq:g_truncation} is overdetermined, a solution may not
exist. Typically, either \textit{Galerkin projection} or \textit{least-squares
Petrov--Galerkin projection} is employed to reduce the number of equations
such that a unique solution exists. We now describe these two methods.

@@

At each time instance on the time grid, the LSPG method substitutes the \spatialAcronym\ trial subspace approximation
\eqref{eq:affine_trialspace} into the FOM O$\Delta$E~\eqref{eq:lms} and
minimizes the residual, i.e., LSPG sequentially computes the solutions
$\approxstateLSPG^n \approx \stateFOMDiscreteArg{n}$, $n=1,\ldots,
\ntimeSteps$ that satisfy
\begin{equation*}
\approxstateLSPG^n = \underset{\stateyDiscrete \in \trialspace  }{\text{arg\,min}}|| \lspgWeightingArg{\stateyDiscrete}\residLMSArg{n} (\stateyDiscrete; \approxstateLSPG^{n-1},\ldots,\approxstateLSPG^{n-k^n}) ||_2, \qquad n = 1,\ldots,\ntimeSteps,
\end{equation*}
where 
$\lspgWeightingArg{\cdot} \in \RR{\nsamples \times \fomdim}$, with $\romdim
\le \nsamples \le \fomdim$, is a weighting matrix that can be used, e.g., to
enable hyper-reduction by requiring it to have a small number of nonzero
columns.

As described in the introduction, although numerical experiments have
demonstrated that LSPG projection often yields more accurate and stable
solutions than Galerkin
projection~\cite{bui_thesis,carlberg_lspg_v_galerkin,carlberg_gnat,carlberg_thesis,parish_apg},
LSPG still suffers from several shortcomings, in particular its complex
dependence on the time discretization, exponentially growing error bounds, and
a lack of optimality for the trajectory defined over the entire time domain.

\subsection{\spaceTimeAcronym\ trial spaces and space--time ROMs}

Space--time projection methods that employ \spaceTimeAcronym\ trial
spaces~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC,benner_st,bui_thesis}
aim to overcome the latter two shortcomings of LSPG projection, which are
shared by all model-reduction methods based on spatial projection followed by
time integration.  Because these methods employ \spaceTimeAcronym\ trial
spaces, they reduce both the spatial and temporal dimensions of the full-order
model; further, they yield error bounds that grow more slowly in time and
their trajectories exhibit an optimality property over the entire time domain.

\spaceTimeAcronym\ trial subspaces approximate the FOM ODE solution
trajectory
	$\stateFOM\in\RR{N}\otimes \timeSpace$ with an approximation that resides in an
	affine space--time trial subspace of dimension $\stdim\ll\fomdim$, i.e., 
	$\approxstate\in \stspaceST$ with $\dim(\stspaceST) =\stdim $, where
\begin{equation}\label{eq:sttrialspace_def}
 \stspaceST \defeq 
	\Range{\stbasis} + 
	\stateIntercept\otimes\onesFunction
	\subseteq \RR{N} \otimes \timeSpace
\end{equation}
and $\stbasis\in\RR{N \times \stdim}\otimes \timeSpace$ with 
$\stbasis:\timeDummy\mapsto\stbasis(\timeDummy)$
denotes the space--time trial basis.

Thus, at any time instance $t\in[0,T]$, ROMs that employ the
\spaceTimeAcronym\ trial subspace approximate the state as
\begin{equation}\label{eq:stapprox1}
 \stateFOMArg{}{t} \approx \approxstateArg{}{t}  = \stbasisArg{}{t} \stgenstate + \stateInterceptArg{},
\end{equation}
where $\stgenstateArg{} \in \RR{\stdim}$ denote the space--time generalized coordinates. 
Critically, comparing the approximations arising from \spatialAcronym\ and
\spaceTimeAcronym\ subspaces in Eqs.~\eqref{eq:affine_trialspace} and \eqref{eq:stapprox1}, respectively,
highlights that the former approximation associates with a time-dependent
generalized coordinates, while the latter approximation associates with a
time-dependent basis matrix.

\KTC{HERE}
Substituting the approximation~\eqref{eq:stapprox1} into the FOM
ODE~\eqref{eq:FOM} yields
\begin{equation}\label{eq:st_fom}
\stbasisDotArg{}{t} \stgenstate =  \velocity(\stbasisArg{}{t} \stgenstate + \stateIntercept,t) , \qquad \genstate(0) =\mathbb{P}(\stateFOM)(0), \qquad t \in [0,T],
\end{equation}
where 
$\stbasisDot\equiv d\stbasis/d\timeDummy$,
$\mathbb{P} : \RR{N} \otimes \timeSpace \rightarrow \stspaceST$ is an orthogonal projection onto the trial subspace (e.g., $\elltwo$).
Equation~\eqref{eq:st_fom} is an over-determined algebraic system for the $\stdim$ unknowns. We now outline the Space--Time Least-Squares Petrov--Galerkin method~\cite{choi_stlspg}. 
The space--time Galerkin method is noted to additionally be a possibility for model reduction. As the space--time Galerkin method does not associate with any residual minimization 
principle, however, we do not outline it here.
\subsubsection{Space--Time LSPG projection}  
As in LSPG, Space--Time LSPG (ST-LSPG)~\cite{choi_stlspg} minimizes the fully discrete residual, with the key difference being that ST-LSPG minimizes the residual over the entire time domain. For brevity, ST-LSPG is outlined only for linear multistep methods.
%As ST-LSPG acts on the discrete solution, we first note that the discrete FOM solution lives in $\RR{N} \otimes \RR{N_t}$. ST-LSPG then seeks solutions in the trial space,
%$$\stspaceDiscrete \defeq \spaceTrialSpace \otimes \timeTrialSpaceDiscrete \subseteq \RR{N} \otimes \RR{N_t},$$
%where $\timeTrialSpaceDiscrete$ is the discrete temporal trial space. It is noted that this trial space is a specific instance of the trial space~\ref{eq:sttrialspace_def} 
%As before, we define a discretization of the continuous time-domain $[0,T]$ into $N_t$ time instances $t^n = n\Delta t, n=1,2,\ldots,N_t$ with a constant time-step $\Delta t = T/N_t$. We define now the space--time discrete residual for the implicit Euler method as,
We first define the space--time discrete residual for linear multistep methods,
\begin{align*}
\residST_{} & \vcentcolon (\stateyDiscreteArg{N_t}, \ldots ,\stateyDiscreteArg{1};\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{N_t}(\stateyDiscreteArg{N_t};\stateyDiscreteArg{N_t-1},\ldots,\stateyDiscreteArg{N_t - k^{N_t}}) \\ 
%\frac{\stateyDiscreteArg{N_t-1} - \stateFOMDiscreteArg{N_t-2}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t-1}) \\
\vdots \\
%\frac{\stateyDiscreteArg{1} - \stateFOMIC }{\Delta t} -  \velocity(\stateyDiscreteArg{1}) \\
\residLMSArg{1}(\stateyDiscreteArg{1}; \stateFOMIC) 
\end{bmatrix}  \\
& \vcentcolon \RR{\fomdim} \otimes \RR{N_t+1} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
For convenience we define the same residual with the generalized coordinates as the inputs,
\begin{align*}
\genresidST_{\text{}} & \vcentcolon (\stgenstatey ;\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{n}\bigg( \stbasisArg{}{t^{N_t}}\stgenstatey + \stateIntercept; \stbasisArg{}{t^{N_t-1}}\stgenstatey + \stateIntercept ,\ldots,  \stbasisArg{}{t^{N_t-k^{N_t}}}\stgenstatey + \stateIntercept \bigg) \\ 
\vdots \\
\residLMSArg{n}\bigg( \stbasisArg{}{t^1}\stgenstatey + \stateIntercept; \stateFOMIC \bigg) \\ 
\end{bmatrix}  \\
& \vcentcolon \RR{\stdim} \times \RR{N} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
ST-LSPG is defined as,
\begin{equation*}
\stgenstate = \underset{ \stgenstatey }{\text{arg\,min}}|| \lspgWeightingSTArg{\stgenstatey}  \genresidST_{\text{}}(\stgenstatey;\stateFOMIC) ||_2^2, 
\end{equation*}
where $\lspgWeightingSTArg{\cdot} \in \RR{n_{st} \times N N_t}$, with $\stdim \le n_{st} \le N N_t$, is a space--time weighting matrix.
